%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textbf{SKILLS}: Python, PHP, MySQL, jQuery, TMDB API, RAWG API, Pandas, HTML, CSS, JavaScript, AJAX, Git} % Skills
    {What You Doin' Right Now (Complex Social Network for Entertainment)} % Event
    {3 Months} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a secure social networking site with authentication and verification, featuring personal media tracking with stats, badges, import-export, diary, feed, mutual media showcase and an admin panel for Movies, TV Shows, Video Games, Books, and Music.}
        \item {Led a team of 6 as an Agile Scrum Master and handled project life cycle including as debugging, security, system design, API requests, and report generation to ensure successful project builds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{SKILLS}: Python, SQLite3, Matplotlib, Seaborn, SpaCy, NLP, BeautifulSoup, Tensorflow, Typer, Pytest} % Skills
    {VocabCLI (Text Processing, Word Store and NLP Command Line Interface)} % Event
    {2 Months} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Crafted a Lightweight CLI for Dictionary Lookups, Vocabulary Building, Quote Saving with Rich Markup, Graph Reporting, Flashcard Study and NLP sticking to Tensorflow and SpaCy for utility functions and Typer for quizzes and revision right inside the terminal.}
        \item{Full PyTest unit, stress, and API endpoint testing coverage. Built MKDocs with Docstrings and packaged as a pip3 installable.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {\textbf{SKILLS}: Python, Django, PostgreSQL, Geolocation and PayPal API, JavaScript, AWS, HTML, BootstrapCSS, AJAX, Git} % Skills
    {FoodOnline (Django Multi Vendor Restaurant Web-App)} % Event
    {4 Months} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Deployed a multi-vendor platform using Python and Django Framework with vendor registration, authentication, marketplace, location based search, payment gateway integration and order management.}
        \item{Implemented menu builder, cart management, dynamic business hours, tax modules, and email templates.}
        \item{Configured PostgreSQL and pushed to production, ensuring successful deployment in a real-world use case with comprehensive testing.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
